\documentclass[a4paper,10pt]{article}

%------------------------- PACKAGES ------------------------- %
% page margins
\usepackage[top = 1.5cm, bottom = 1.5cm, left = 1.5cm, right = 1.5cm]{geometry}

\usepackage{titlesec}

% required for tables
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{caption}
\captionsetup[table]{skip=10pt}

% required for images
\usepackage{graphicx}
\usepackage{subfig}

% required to fix paragraph auto-indent
\usepackage{setspace}
\setlength{\parindent}{0in}

% place images where you want
\usepackage{float}

% required for nice headers
\usepackage{fancyhdr}

% % required for generating links for ToC
% \usepackage{hyperref}
\usepackage[hidelinks]{hyperref}

% required for showing code
\usepackage{listings}
\usepackage{xcolor}

% For author affiliations
\usepackage{authblk}

\definecolor{darkblue}{RGB}{0,0,139}
\definecolor{golden}{rgb}{0.85, 0.65, 0.13}

\usepackage{sectsty}
\sectionfont{\color{darkblue}}
\subsectionfont{\color{darkblue}}
\subsubsectionfont{\color{darkblue}}

% ----------------------------------------------------------- %

%-------------------- HEADER & FOOTER ----------------------- %
\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{darkblue}{\footnotesize CS7IS5 - Adaptive Systems: Project Outline}}
\rhead{\textcolor{darkblue}{\footnotesize Fitness Companion - Team Aphrodite}}
\cfoot{\footnotesize \thepage}
% ----------------------------------------------------------- %

%----------------------- DOCUMENT --------------------------- %
\begin{document}

% disable header on first page
\thispagestyle{empty}
% table for first page header
\textcolor{darkblue}{
    \begin{tabular}{p{17.5cm}}
        {\large \bf CS7IS5 - Adaptive Systems} \hfill Trinity College Dublin \\
        \hfill Hilary Term 2024 \\
        \\
        \hline
        \vspace*{0.05cm}
         Aadesh\ Rasal \hfill Anupal\ Mishra        \\
         (xyz@tcd.ie, 12345678) \hfill (anmishra@tcd.ie, 23332008) \\
         \vspace*{0.02cm}
         Frason\ Kalapurackal \hfill Juliette\ Van\ Marken        \\
         (xyz@tcd.ie, 12345678) \hfill (xyz@tcd.ie, 12345678) \\
        % \hline
    \end{tabular}
}
\vspace*{0.2cm}

\begin{center}
    {\Large \bf Fitness Companion - Project Outline}
    \vspace{2mm}
\end{center}

\tableofcontents

\section{Project Goals and Motivation}

% problem statement and motivation
% points: plethora of info, users abandon goals, apps don't combine both, easily consumable, user-driven

In the last decade and a half, an increasing number of people have become aware of the health benefits associated with maintaining a regular fitness routine, which include enhanced productivity and happiness.
While this awareness serves as an incentive for individuals to establish fitness objectives, the overwhelming amount of information available online often becomes a hindrance.
Most success stories involve consistent gym attendance and the guidance of a personal trainer, both of which can come with significant membership fees.
Moreover, there are only a few applications available that offer both workout routines and diet plans.
As a result, most individuals tend to abandon their fitness goals.

To address this challenge, we propose a user-centric fitness tracking application that provides straightforward and accessible information. \\

We define following as our core project goals:

\begin{itemize}
    \item Enable users to define fitness goals and monitor progress.
    \item Users receive customizable recommendations for gym workouts and dietary plans.
\end{itemize}

The following enhancements will be introduced as optional features, subject to time constraints:
\begin{itemize}
    \item Recipies for dishes that are included in diet plan recommendations.
    \item Adaptive search engine for the user to interact with the application instead of filling a questionnaire.
\end{itemize}

\pagebreak

\section{Technical Summary and Proposed Architecture}

\section{Roles \& Responsibilities}

\section{Timeline}

\section{AI Tools}
We did not make use of AI tools in the preparation of this project.

\end{document}